\input{title.tex}

### 2022-04-26 docs/papers/01_manuscript/04_discussion.tex
fix(contextplot.ipynb,-discussion.py,-config.py): re-plot, grammarly fix, use bidict,

% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions.
Moreover, we report how another institutional shift contributed to successful water governance  -the subsequent success of 98-UBR has proved the importance of social-ecological fit again, theoretically and practically.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential in resulting in better water governance.
In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.

>>>>

% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions.
Moreover, we report how another institutional shift contributed to successful water governance  -the subsequent success of 98-UBR has proved the importance of social-ecological fit again, theoretically and practically.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.
